---
title: "Sublime Git Tutorial"
author: "rebecca hayes"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Using Sublime Merge for GitHub  



1. Download Sublime Merge for Windows or Mac OS  

Mac installation https://www.sublimemerge.com/download_thanks?target=mac

Windows installation https://www.sublimemerge.com/download_thanks?target=win-x64


2. Clone repository
Sign into GitHub
Add SHA id from your personal laptop?
Link

3. Open text file (.txt) and type your answers to the following questions:

4. Save as 'Firstname_LastInitial.txt' and add commit message (conventional commits)
https://gist.github.com/Zekfad/f51cb06ac76e2457f11c80ed705c95a3

5. Push and pair up! 

6. Pull from the remote to your local. Open your partner's document. Change question 2. 

7. Push to remote! 

8. Notice the arrows in sublime merge.

9. Dealing with merge conflicts.

10. Where to learn more:








```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
